---
title: "Comparing Marriott and Hilton Sentiments on Twitter"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
## Sentiments
The following graphs display the sentiment of tweets over the past 7 days. The data gathered starts on November 30th 2018, which was the day Marriott went public with the news of its massive data breach.
```{r setup, echo=FALSE,warning=FALSE, message=FALSE}
# knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(readr)
library(scales)
library(ggplot2)
library(lubridate)
library(hash)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(tidyverse)
library(grid)
library(gridExtra)

setwd("C:\\Users\\Michelle Dezihan\\Desktop\\BMKT670-Applied-Data-Analytics\\ada-project-1\\")
marriott <- read.csv("clean_tweets.csv")
hilton <- read.csv("hilton_clean_tweets.csv")

## FUNCTIONS ##
stopword_hash <- hash(keys=stopwords('english'), values=TRUE)
fast_replace_stopword <- function(doc) {
  # Get doc text and split into list of words
  text <- content(doc[[1]])
  words <- strsplit(text, " ")[[1]]
  words <- words[words != ""]
  
  nonstop_words <- vector(mode = "list", length = length(words))
  nonstop_words_index <- 1
  for(word in words) {
    is_stop_word = stopword_hash[[word]]
    
    if (is.null(is_stop_word)) {
      nonstop_words[nonstop_words_index] <- word
      nonstop_words_index = nonstop_words_index + 1
    }
  }
  nonstop_words <- compact(nonstop_words)
  docs <- Corpus(VectorSource(paste0(nonstop_words, collapse=' ')))
  dtm <- TermDocumentMatrix(docs)
  m <- as.matrix(dtm)
  v <- sort(rowSums(m),decreasing=TRUE)
  return(docs)
}

create_wordcloud <- function(text) {
  docs <- Corpus(VectorSource(text))
  toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
  docs <- tm_map(docs, toSpace, "/")
  docs <- tm_map(docs, toSpace, "@")
  docs <- tm_map(docs, toSpace, "\\|")
  docs <- tm_map(docs, content_transformer(tolower))
  docs <- tm_map(docs, removeNumbers)
  docs <- tm_map(docs, removePunctuation)
  docs <- tm_map(docs, stripWhitespace)
  docs <- fast_replace_stopword(docs)
  dtm <- TermDocumentMatrix(docs)
  m <- as.matrix(dtm)
  v <- sort(rowSums(m),decreasing=TRUE)
  d <- data.frame(word = names(v),freq=v)
  head(d, 10)
  return(d)
}
```

```{r, echo=FALSE,warning=FALSE, message=FALSE}
marriott <- marriott %>% mutate(count=1:length(Timestamp))
hilton <- hilton %>% mutate(count=1:length(Timestamp))

m_plot <- ggplot(marriott,aes(x=count,y=Sentiment)) + 
  geom_line() + 
  scale_y_continuous() +
  labs(x="",y="Sentiment Score")

h_plot <- ggplot(hilton,aes(x=count,y=Sentiment)) +
  geom_line()+
  scale_y_continuous() +
  labs(x="",y="Sentiment Score")

grid.arrange(m_plot,h_plot)
```

##WordClouds
For Marriott, the most frequent words mentioned in tweets are unsurprisingly "data","breach", and "million." Notable mentions also include "security" and "hack." For Hilton, the most frequent words appear to be related to the location of the hotel, events, and charity terms such as "Freecember", "toy" and "drive."

```{r, echo=FALSE,warning=FALSE, message=FALSE}
par(mfrow=c(1,2))
m <- marriott %>%
  summarise(Tweet=paste0(Tweet,collapse=" "))
m_wordcloud <- create_wordcloud(m[[1]])

set.seed(456)
wordcloud(words = m_wordcloud$word, freq = m_wordcloud$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))

h <- hilton %>% 
  summarise(Tweet=paste0(Tweet,collapse=" "))

h_wordcloud <- create_wordcloud(h[[1]])

set.seed(456)
wordcloud(words = h_wordcloud$word, freq = h_wordcloud$freq, min.freq = 1,
          max.words=150, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))
```